---
title: "Williams-Celeste-Homework-02.Rmd"
author: "C. Williams"
date: "3/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Challenge 11.1

Every Saturday, at the same time, a primatologist goes and sits in the forest in the morning and listens for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number calls she will hear in that time is 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

###1a) What is the probability that she will hear more than 8 calls during any given session?

```{r ppois}
1-ppois(9, 15)
```
###1b) What is the probability that she will hear no calls in a session?
```{r dpois}
dpois(0,15)
```
###1c) What is the probability that she will hear exactly 3 calls in a session?
``` {r dpois2}
dpois(3,15)  
```
###1d. Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.
``` {r x}
x <- 0:30
l = 15
probset <- dpois(x = x, lambda = l)
barplot(probset, names.arg = x)
```


###1e. Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?


```{r sample}
sample(x, 104,replace = TRUE)
```


###1f. Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?
```{r hist1}
hist(sample(x, 104,replace = TRUE), xlim=c(0,30))
```

####My histogram  doesn't follow a normal distribution like the probability mass function did. It was close to normal, except there was a larger number of observations where 0-5 calls were heard.




#Challenge 11.2

```{r file}
f<-"~/Desktop/zombies.csv"
d <- read.table(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```
###2a) Calculate the population mean and standard deviation for each quantitative random variable (height, weight, age, number of zombies killed, and years of education).

```{r 2asum}
summary(d)
```
``` {r names}
names(d)
```
``` {r mdh}
mean(d$height, na.rm=TRUE)
```
```{ r mdw}
mean(d$weight, na.rm=TRUE)
```
``` {r mda}
mean(d$age, na.rm=TRUE)
```
``` {r mdzk}
mean(d$zombies_killed, na.rm=TRUE)
```
``` {r mdyoe}
mean(d$years_of_education, na.rm=TRUE)
```
``` {r sdh}
sqrt(sum((d$height-mean(d$height))^2)/length(d$height))
```
``` {r sdw}
sqrt(sum((d$weight-mean(d$weight))^2)/length(d$weight))
```
``` {r sda}
sqrt(sum((d$age-mean(d$age))^2)/length(d$age))
```
``` {r sdzk}
sqrt(sum((d$zombies_killed-mean(d$zombies_killed))^2)/length(d$zombies_killed))
```
``` {r sdyoe}
sqrt(sum((d$years_of_education-mean(d$years_of_education))^2)/length(d$years_of_education))
```


###2b)Use {ggplot} and make boxplots of each of these variable by gender.

```{r gg}
library(ggplot2)
```
```{r t hvg}
ggplot(d, aes(x=gender, y=height)) + geom_boxplot()
```
```{r gg gvw}
ggplot(d, aes(x=gender, y=weight)) + geom_boxplot()
```
```{r gva}
ggplot(d, aes(x=gender, y=age)) + geom_boxplot()
```
``` {r gvyed}
ggplot(d, aes(x=gender, y=years_of_education)) + geom_boxplot()
```
``` {r ggplotgvszk}
ggplot(d, aes(x=gender, y=zombies_killed)) + geom_boxplot()
```
``` {r ggplotgvcyed}
ggplot(d, aes(x=gender, y=years_of_education)) + geom_boxplot()
```



###2c)Use {ggplot} and make scatterplots of height and weight in relation to age. Do these variables seem to be related? In what way?

```{r ggplot avh}
ggplot(data = d, aes(x = age, y=height)) + geom_point()
```
``` {r ggployavw}
ggplot(data = d, aes(x = age, y=weight)) + geom_point()
```


####Height and weight both seem to have a positive correlation with age, as age increases so does height and weight. However, there appears to be a stronger relationship between height and age



###2d) Using histograms and Q-Q plots, check whether the quantitative variables seem to be drawn from a normal distribution. Which seem to be and which do not?

###Height
```{r histqq height}
summary(d$height)
hist(d$height, breaks = seq(from=50, to=85, by=.5))
qqnorm(d$height, main = "QQ Plot- Height")
qqline(d$height)
```

###Weight
```{r hidtqq weight}
summary(d$weight)
hist(d$weight, breaks = seq(from=85, to=215, by=1))
qqnorm(d$weight, main = "QQ Plot- Weight")
qqline(d$weight)
```

###Age
``` {r histqq age}
summary(d$age)
hist(d$age, breaks = seq(from=10, to=30, by=.5))
qqnorm(d$age, main = "QQ Plot- Age")
qqline(d$age)
```

###Years of Education
``` {r histqq edu}
summary(d$years_of_education)
hist(d$years_of_education, breaks = seq(from=0, to=10, by=1))
qqnorm(d$years_of_education, main = "QQ Plot- Years of Education")
qqline(d$years_of_education)
```

###Zombies Killed
``` {histqq zombies killed}
summary(d$zombies_killed)
hist(d$zombies_killed, breaks = seq(from=0, to=11, by=1))
qqnorm(d$zombies_killed, main = "QQ Plot- Zombies Killed")
qqline(d$zombies_killed)
```

####Height, weight, and age seem to be drawn from a normal distribution, whereas years of education and zombies killed do not.



###2e) Now use the sample() function to sample ONE subset of 30 zombies (without replacement) from this population and calculate the mean and sample standard deviation for each variable. Also estimate the standard error for each variable and construct the 95% confidence interval for each mean. Note that for the variables that are not drawn from the normal distribution, you will need to base your estimate of the CIs on some different distribution!

``` {r sciplot, echo=FALSE}
library(sciplot)
```
``` {r sample 1}
Z<- d[sample(nrow(d),30),]
Z
```
###Height

```{r sample 1 height data}
mean(Z$height)
sd(Z$height)
se(Z$height)
qnorm(0.025, mean(Z$height), sd(Z$height)) 
qnorm(0.975,mean(Z$height),sd(Z$height))
```

###Weight
```{r sample 1 weight data}
mean(Z$weight)
sd(Z$weight)
se(Z$weight)
qnorm(0.025, mean(Z$weight), sd(Z$weight))
qnorm(0.975,mean(Z$weight),sd(Z$weight))
```

###Zombies Killed
``` {r sample 1 zombies killed data}
mean(Z$zombies_killed)
sd(Z$zombies_killed)
se(Z$zombies_killed)
quantile(Z$zombies_killed, c(0.025, 0.975))
summary(Z$zombies_killed)
```

###Years of Education
``` {r sample 1 education data}
mean(Z$years_of_education)
sd(Z$years_of_education)
se(Z$years_of_education)
quantile(Z$years_of_education, c(0.025, 0.975))
summary(Z$years_of_education)
```

###Age
```{r sample 1 age data}
mean(Z$age)
sd(Z$age)
se(Z$age)
qnorm(0.025, mean(Z$age), sd(Z$age))
qnorm(0.975,mean(Z$age),sd(Z$age))
```



###2f) Now draw 99 more random samples of 30 zombie apocalypse survivors out and calculate the mean for each of the these samples. Together with the first sample you drew out, you now have a set of 100 means for each variable (each based on 30 observations), which constitutes a sampling distribution for each variable. What are the means and standard deviations of the sampling distribution for each variable? How do the standard deviations compare to the standard errors estimated in [2.e.]? What do these sampling distributions look like? Are they normally distributed? What about for those variables that you concluded were not originally drawn from a normal distribution?

``` {r 99 sample}
k <- 99  
n <- 30  
s <- NULL  
for (i in 1:k) {
  s[[i]] <- d[sample(nrow(d),30),]
}
```

###Height
```{r 99 height}
Mean_Height<-NULL
for (i in 1:k) {
  Mean_Height[i]<- mean(s[[i]]$height)
}
Mean_Height 
```

###Weight
```{r 99 weight}
Mean_Weight<-NULL
for (i in 1:k) {
  Mean_Weight[i]<- mean(s[[i]]$weight)
}
Mean_Weight
```

###Age
``` {r 99 age}
Mean_Age<-NULL
for (i in 1:k) {
  Mean_Age[i]<- mean(s[[i]]$age)
}
Mean_Age
```

###Zombies Killed
```{r 99 zombies killed}
Mean_Zombies_Killed<-NULL
for (i in 1:k) {
  Mean_Zombies_Killed[i]<- mean(s[[i]]$zombies_killed)
}
Mean_Zombies_Killed
```

###Years of Education
``` {r 99 edu}
Mean_Years_Education<-NULL
for (i in 1:k) {
  Mean_Years_Education[i]<- mean(s[[i]]$years_of_education)
}
Mean_Years_Education
```

``` {r res1, echo=FALSE}
res1 <-c(mean(Z$height),mean(Z$weight), mean(Z$age),mean(Z$zombies_killed), mean(Z$years_of_education))
```
``` {r nnsamp, echo=FALSE}
nnsamp<- cbind(Mean_Height, Mean_Weight, Mean_Age, Mean_Zombies_Killed, Mean_Years_Education)
```
```{r bind, echo=FALSE}
zsamp<- rbind(res1)
```
```{r bind all, echo=FALSE}
zzsamp<- rbind (nnsamp, zsamp)
```
```{r bind all as data frame}
zzsamp<- as.data.frame(zzsamp)
zzsamp
```

###Height
``` {r 100 height data}
mean(zzsamp$Mean_Height)
sd(zzsamp$Mean_Height)
se(Z$height)
hist(zzsamp$Mean_Height)
```

###Weight
``` {r 100 weight data}
mean(zzsamp$Mean_Weight)
sd(zzsamp$Mean_Weight)
se(Z$weight)
hist(zzsamp$Mean_Weight)
```

###Age
```{r 100 age data}
mean(zzsamp$Mean_Age)
sd(zzsamp$Mean_Age)
se(Z$age)
hist(zzsamp$Mean_Age)
```

###Zombies Killed
``` {r 100 zombies killed data}
mean(zzsamp$Mean_Zombies_Killed)
sd(zzsamp$Mean_Zombies_Killed)
se(Z$zombies_killed)
hist(zzsamp$Mean_Zombies_Killed)
```

###Years of Education
``` {r 100 years edu data}
mean(zzsamp$Mean_Years_Education)
sd(zzsamp$Mean_Years_Education)
se(Z$years_of_education)
hist(zzsamp$Mean_Years_Education)
```

#### The variables that didn't appear to follow a normal distribution, now look more like one. 






